Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-01-14 paper/zhang-cook-laa-langrene-menendez.Rmd
writing on explore_trace_interp()

```{r toy-interp, fig.cap = "Trace plots of two optimisation procedures with color representing each iteration. The first optimiser progresses monotonically towards the opitmum while the second has experienced some reduction in some iterations."}
```

Points on the interpolation path are another interest in tour since the projection on these bases will be played by the tour animation. Figure \ref{fig:toy-interp} presents the interpolation of two different tour paths. The interpolation on the left has index value increase monotonically while the right one has the index value decreases in several iteration. Compare to the Figure \ref{fig:toy-search}, Figure \ref{fig:toy-interp} provides additional information on how the interpolation gradually reaches the target basis in each iteration: either monotonically or experiencing a turning point, as seen on the right of Figure \ref{fig:toy-interp}.

>>>>

```{r toy-interp, fig.cap = "Trace plots of the bases on the interpolation path for two optimisers with the same configuration as the previous figure. The right path shows that to reach a lower target basis, the interpolation actually first passes some higher basis and this could potentially be information to be incorporated into the optimisers."}
```

Viewing the index value of points on the interpolation path is another interest to the analysts since the projection on these bases will be played by the tour animation and it provides further information on how the index value changes when moving from one target basis to another. Figure \ref{fig:toy-interp} presents the index value against time on the interpolation path for the two optimisers with same configuration as \ref{fig:toy-search}. From Figure \ref{fig:toy-interp}, we further know that to reach a target basis with lower index value, the optimiser plotted on the right  first passes some bases with higher index value during the interpolation. If the bases on the interpolation path can be incorporated into the optimisation, we may be able to find the optimal basis quicker.

### 2021-01-14 paper/zhang-cook-laa-langrene-menendez.tex
writing on explore_trace_interp()

\caption[Trace plots of two optimisation procedures with color representing each iteration]{Trace plots of two optimisation procedures with color representing each iteration. The first optimiser progresses monotonically towards the opitmum while the second has experienced some reduction in some iterations.}\label{fig:toy-interp}
\end{figure}
\end{Schunk}

Points on the interpolation path are another interest in tour since the
projection on these bases will be played by the tour animation. Figure
\ref{fig:toy-interp} presents the interpolation of two different tour
paths. The interpolation on the left has index value increase
monotonically while the right one has the index value decreases in
several iteration. Compare to the Figure \ref{fig:toy-search}, Figure
\ref{fig:toy-interp} provides additional information on how the
interpolation gradually reaches the target basis in each iteration:
either monotonically or experiencing a turning point, as seen on the
right of Figure \ref{fig:toy-interp}.

>>>>

\caption[Trace plots of the bases on the interpolation path for two optimisers with the same configuration as the previous figure]{Trace plots of the bases on the interpolation path for two optimisers with the same configuration as the previous figure. The right path shows that to reach a lower target basis, the interpolation actually first passes some higher basis and this could potentially be information to be incorporated into the optimisers.}\label{fig:toy-interp}
\end{figure}
\end{Schunk}

Viewing the index value of points on the interpolation path is another
interest to the analysts since the projection on these bases will be
played by the tour animation and it provides further information on how
the index value changes when moving from one target basis to another.
Figure \ref{fig:toy-interp} presents the index value against time on the
interpolation path for the two optimisers with same configuration as
\ref{fig:toy-search}. From Figure \ref{fig:toy-interp}, we further know
that to reach a target basis with lower index value, the optimiser
plotted on the right first passes some bases with higher index value
during the interpolation. If the bases on the interpolation path can be
incorporated into the optimisation, we may be able to find the optimal
basis quicker.
